A general and efficient representation of Ancestral Recombination Graphs

### 2022-09-01 paper.tex
Add shipilina et al and some places to mention

\section*{When do we need ``full'' ARGs?}
% The full ancestral recombination graph (ARG) is a structure that encodes all
% coalescence and recombination events resulting from the stochastic process of
% the coalescent with recombination.
\citet{brandt2021evaluation} define a ``full'' ARG as
``a structure that encodes all
coalescence and recombination events resulting from the stochastic process of
the coalescent with recombination'' (thus going against the general
historial trend discussed in the XXX section).
\citet{rasmussen2022espalier} have a less restrictive definition, in
which a ``full'' ARG is one that contains complete information about
recombination events, without necessarily being tied to a particular
stochastic process.
While [something positive], it is important to be clear on
what the overall goal of such precise inferences are, and
on the realistic limitations are on when they can be made.

@@

@@

>>>>

\section*{When do we need ``full'' ARGs?}
% The full ancestral recombination graph (ARG) is a structure that encodes all
% coalescence and recombination events resulting from the stochastic process of
% the coalescent with recombination.
\citet{brandt2021evaluation} define a ``full'' ARG as
``a structure that encodes all
coalescence and recombination events resulting from the stochastic process of
the coalescent with recombination'' (thus going against the general
historial trend discussed in the XXX section).
\citet{rasmussen2022espalier} have a less restrictive definition, in
which a ``full'' ARG is one that contains complete information about
recombination events, without necessarily being tied to a particular
stochastic process.
While [something positive], it is important to be clear on
what the overall goal of such precise inferences are,
what the limitations on when they can be made are,
and their downstream utility in applications.

@@

% Is it practical to estimate full ARGs?
[Not particularly \citep{shipilina2022origin}]

@@

\item This idea of a continuum of information about recombination
being inferrable and representable is consistent with the ideas
discussed by~\cite{shipilina2022origin}. There a haplotype block
is synonymous with coalescent nodes in the ARG, which we can generalise
as nodes in a gARG with at least two children. In principle, these
nodes are identifiable by the mutations that occur on the outbound
edges of the node.
Their definition of an ARG is interesting, as they emphasise that it
is composed of events, but illustate the genomes. [Nice to mention
this connection somehere if we can, see Fig B1]
